---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = FALSE,
  comment = "#>",
  message = FALSE,
  error = FALSE,
  warning = FALSE,
  fig.path = "README/README-",
  fig.width=7.3,
  fig.height=5,
  out.width = '100%'
)
```

## Description

`gtsf` is an R package for using GTFS data as [simple features](https://en.wikipedia.org/wiki/Simple_Features). You can also use it to make shapefiles and geojson from GTFS data.  

## Installation

You can install this package from GitHub using the devtools package:

```
if (!require(devtools)) {
    install.packages('devtools')
}
devtools::install_github('r-gtfs/gtsf')
```

## Example Usage 

Import transit lines from the NYC Subway using `tread`.

```{r readme-body}
library(tread)
library(gtsf)
library(dplyr)

NYC <- import_gtfs("http://web.mta.info/developers/data/nyct/subway/google_transit.zip")
```

## Get Simple Features

```{r}
NYC <- gtfs_as_sf(NYC)
```

This adds two simple features dataframes to the list of GTFS objects:
-stops_sf 
-routes_sf

## Make Maps

These can be mapped with various libraries. For example, with the [tmap](https://cran.r-project.org/web/packages/tmap/vignettes/tmap-nutshell.html) package:

```{r}
library(tmap)
routes_sf <- NYC$sf_routes
qtm(routes_sf)
```

## Export (GeoJSON/Shapefile)

They can also be exported to geojson, for use elsewhere. For example:

```{r}
library(sf)
st_write(NYC$sf_routes,"nyc_routes.geojson", delete_dsn = TRUE)
```
